\begin{enumerate}
    
    \section*{General questions}

    \item Are you familiar with the Music Information Retrieval field of research?
    \begin{itemize}[label=$\circ$]
        \item Yes
        \item No
    \end{itemize}

    \item When did you first hear about the AcousticBrainz project?
    \begin{itemize}[label=$\circ$]
        \item 2014
        \item 2015
        \item 2016
    \end{itemize}
    
    \item Have you used the AcousticBrainz client to extract and submit data from your music collection? \\
    \textit{GUI or CLI client from \url{https://acousticbrainz.org/download}.}
    \begin{itemize}[label=$\circ$]
        \item Yes
        \item No
    \end{itemize}

    \section*{Datasets and evaluation}

    \item How many datasets have you created? \\
    \textit{Either using the web editor or CSV importer.} \\
    $\_\_\_\_$

    \item What interface have you used to create dataset(s)?
    \begin{itemize}[label=$\square$]
        \item Web-based editor
        \item CSV importer
        \item Both web-based editor and CSV importer
        \item I didn't create any datasets
    \end{itemize}

    \item How many datasets have you submitted for evaluation? \\
    $\_\_\_\_$

    \item Ease of use \\
    \textit{Please choose how easy it was to use each feature. You can account for aspects such as interface being intuitive, terminology used, data presented in the interface, etc.} \\
    \\
    {\footnotesize
    \begin{tabularx}{\textwidth}{ X | X | l | X | l | l | X }
        & Very difficult & Difficult & Neither easy nor difficult & Easy & Very easy & I didn't use this feature \\
        \hline Dataset editor & & & & & & \\
        \hline CSV importer & & & & & & \\
        \hline Dataset viewer & & & & & & \\
        \hline Evaluation submission interface & & & & & & \\
        \hline Evaluation results viewer & & & & & & \\
    \end{tabularx}
    }

    \item How would you improve the dataset creation process? \\
    \textit{Feel free to provide additional thoughts about dataset creation feature. What problems you encountered, what can be improved, etc.} \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$

    \item How would you improve the evaluation interface? \\
    \textit{Feel free to provide additional thoughts about dataset evaluation interface. What problems you encountered, what can be improved, etc.} \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$

    \section*{Dataset creation challenges}

    \item Have you submitted your dataset(s) for the "Classifying vocals" challenge? \\
    \textit{\url{https://beta.acousticbrainz.org/challenges/14095b3b-4469-4e4d-984e-ef5f1a55962c}} \\
    \begin{itemize}[label=$\circ$]
        \item Yes
        \item No
    \end{itemize}

    \item How well did you understand the challenge process? \\
    \textit{Creation of a dataset with a specific structure for a challenge. Submission of a dataset for a challenge. Results of a challenge. \\
    Specify a number from 0 to 4. 0 - Didn't understand at all. 4 - Understood everything.} \\
    $\_\_\_\_$

    \item If you didn't understand everything, which parts were unclear?
    \begin{itemize}[label=$\square$]
        \item Dataset structure requirements
        \item Submission process
        \item Results calculation
        \item Other $\_\_\_\_\_\_\_\_\_\_$
    \end{itemize}
    
    \item Ease of use \\
    \textit{Please choose how easy it was to use each feature. You can account for aspects such as interface being intuitive, terminology used, data presented in the interface, etc.} \\
    \\
    {\footnotesize
    \begin{tabularx}{\textwidth}{ X | X | l | X | l | l | X }
        & Very difficult & Difficult & Neither easy nor difficult & Easy & Very easy & I didn't use this feature \\
        \hline Submission of datasets for a challenge & & & & & & \\
        \hline Challenge details page & & & & & & \\
    \end{tabularx}
    }

    \item What improvements related to challenges would you make? \\
    \textit{Feel free to provide additional thoughts about the challenges interface or the process of creating and submitting a dataset for a specific challenge. What problems you encountered, what can be improved, etc.} \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$

    \section*{Feedback collection}
    \textit{Questions here are related to data and interface on recording summary page. Feel free to open it for reference. For example, https://beta.acousticbrainz.org/770cc467-8dde-4d22-bc4c-a42f91e7515e.}

    \item Do you understand the difference between high-level and low-level data? \\
    \textit{This information is presented on a summary page for each recording.} \\
    \begin{itemize}[label=$\circ$]
        \item Yes
        \item No
    \end{itemize}
    
    
    \item Do you know what the following concepts mean? \\
    \textit{See "High-level information" section on a summary page for example of their usage.} \\
    \\
    {\footnotesize
    \begin{tabularx}{\textwidth}{ X | c | c | c }
        & No & Not sure & Yes \\
        \hline Vocals & & & \\
        \hline Gender & & & \\
        \hline Danceability & & & \\
        \hline Tonality & & & \\
        \hline Timbre & & & \\
        \hline Rhythm & & & \\
        \hline Genre & & & \\
        \hline Mood & & & \\
    \end{tabularx}
    }

    \item Have you tried to submit feedback on high-level data for recordings? \\
    \textit{Feedback can be submitted on a summary page. You need to be logged in! For example, https://beta.acousticbrainz.org/770cc467-8dde-4d22-bc4c-a42f91e7515e.} \\
    \begin{itemize}[label=$\circ$]
        \item Yes
        \item No
    \end{itemize}
    
    \item Ease of use \\
    \textit{Please choose how easy it was to use each feature. You can account for aspects such as interface being intuitive, terminology used, etc.} \\
    \\
    {\footnotesize
    \begin{tabularx}{\textwidth}{ X | X | l | X | l | l | X }
        & Very difficult & Difficult & Neither easy nor difficult & Easy & Very easy & I didn't use this feature \\
        \hline Submission of feedback & & & & & & \\
    \end{tabularx}
    }

    \item What improvements related to the feedback interface would you make?
    \textit{Feel free to provide additional thoughts about data feedback interface. What problems you encountered, what can be improved, etc.} \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$
    
    \section*{Additional information}

    \item Your AcousticBrainz/MusicBrainz username \\
    \textit{Feel free to specify your username so that we can look at your datasets, evaluation results, or challenge submission in case there were some issues.} \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$
    
    \item Anything else you want to say that wasn't covered in this survey \\
    $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$
    
\end{enumerate}
